---
title: "strawberry"
author: "Tao Guo"
date: "2022-11-06"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(readxl)
library(ggplot2)
```

## Cleaning data

Separate the column of Data Item

```{r }
strawb <- read_xlsx("strawberries-2022oct30-a.xlsx",col_names = TRUE)
## separate the Data Item 
strawb2 <- strawb %>% separate(col=`Data Item`,
                               into = c("Strawberries", "items"),
                               sep = "-",
                               fill = "right")
strawb2 %<>% separate(col = `Strawberries`, into = c("Strawberries", "type", "type2"), 
                      sep = ",", fill = "right")
strawb3 <- strawb2 %>% separate(col = `items`, into = c("sale type", "units"), 
                                sep = ",", fill = "right")

strawb4 <- strawb3 %>% select(-c(4, 8:13, 15, 17))
```

1.  Build organic and non organic tibble

```{r }
Domain_organic1 <- grep("organic", 
                       strawb4$Domain, 
                       ignore.case = T)

org_rows1 <- Domain_organic1
strawb_organic <- strawb4 %>% slice(org_rows1, preserve = FALSE)

strawb_non_organic <- strawb4 %>% filter(!row_number() %in% org_rows1)
```

```{r}
strawb_non_organic %<>% pivot_wider(names_from = `units`, values_from = `Value`)
strawb_organic %<>% pivot_wider(names_from = `units`, values_from = `Value`)
```

2.  From non organic, separate the chemical tibble

```{r echo = FALSE}
chem_rows <- grep("BEARING", 
                       strawb_non_organic$type, 
                       ignore.case = T)
chem_rows_1 <- grep("chemical", 
                  strawb_non_organic$Domain, 
                  ignore.case = T)
## chem_rows and chem_row_1 different rows
## firstly I guess the fertilizer in have BEARING is type column, but It is not in Domain 
chem_rows_f <- grep("FERTILIZER", strawb_non_organic$Domain)
intersect(chem_rows_f, chem_rows)
```

```{r}
strawb_chem <- strawb_non_organic %>% slice(chem_rows, preserve = FALSE)
strawb_chem
```

## Poison chemical Carbendazim, Bifenthrin, methyl bromide, 1,3-dichloropropene, chloropicrin, Telone

Searching the Poison chemical mentioned in reading

```{r }
#empty
df_carbendazim <- grep("carbendazim", 
                       strawb_chem$`Domain Category`, ignore.case = T)
df_Bifenthrin <- grep("Bifenthrin", 
                       strawb_chem$`Domain Category`, ignore.case = T)
df_methyl_bromide <- grep("methyl bromide", 
                      strawb_chem$`Domain Category`, ignore.case = T)
#empty
df_1_3_dichloropropene <- grep("1,3-dichloropropene", 
                          strawb_chem$`Domain Category`, 
                          ignore.case = T)
df_chloropicrin <- grep("chloropicrin", 
                               strawb_chem$`Domain Category`, ignore.case = T)
## empty
df_Telone <- grep("Telone", 
                        strawb_chem$`Domain Category`, 
                        ignore.case = T)
```

## Tibble for posion chemicals

The carbendazim, 1_3\_dichloropropene, and Telone did not find in table

```{r }
Bifenthrin <- strawb_chem[df_Bifenthrin,]
methyl_bromide <- strawb_chem[df_methyl_bromide,]
dichloropropene <- strawb_chem[df_chloropicrin,]

```

## Total Posion chemicals by State

```{r echo = FALSE}

Posion_chem <- strawb_chem[c(df_Bifenthrin,df_methyl_bromide,df_chloropicrin ),]


```



```{r }
LB <- ifelse(Posion_chem$` MEASURED IN LB`[1:16]=="(D)",0, Posion_chem$` MEASURED IN LB`[1:16])
LB <- as.numeric(LB)
Posion_chem$` MEASURED IN LB` <- LB
Posion_chem %>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
```

### total chemical using by State

```{r}
LB_total <- ifelse(strawb_chem$` MEASURED IN LB`[1:728]=="(D)"|strawb_chem$` MEASURED IN LB`[1:728]=="(NA)"|strawb_chem$` MEASURED IN LB`[1:728]=="(Z)",0,strawb_chem$` MEASURED IN LB`[1:728])
strawb_chem$` MEASURED IN LB` <- as.numeric(LB_total)
strawb_chem%>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))%>% kable(caption = "Total Posion Chemicals Using by State", digits = 3, format.args = list(big.mark = ",")) %>% kable_minimal(full_width = F)
```

## Percentage poison chemicals by State

```{r}
total_rows <- grep("(TOTAL)", 
strawb_chem$`Domain Category`, ignore.case = T)
fertlizer_rows <- grep("FERTILIZER",strawb_chem$`Domain Category`, ignore.case = T)
chem_total <- strawb_chem[c(total_rows,fertlizer_rows),]
```

```{r}
Posion_state <- Posion_chem %>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
chem_state <- chem_total%>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))

Posion_state$Total_LB <- chem_state$LB_sum
Posion_state %>% mutate(Percent_posion = LB_sum/Total_LB)
percent_posion_state <- Posion_state %>% mutate(Percent_posion = LB_sum/Total_LB)
```

```{r}
percent_posion_state1 <- percent_posion_state[-4] %>% pivot_longer(c(LB_sum,Total_LB), names_to = "type",values_to = "value")
```

```{r}
ggplot(percent_posion_state1, aes(fill=type, y=log(value+1), x=State)) + 
    geom_bar(position="dodge", stat="identity")+ylab("log scale of Measure in LB")+
  ggtitle("Poison Chemicals and Total Chemicals by State")+
  scale_fill_discrete(labels = c("Poison Chemicals","Total Chemicals"))
```

From this plot, The California high weight of poison chemicals than other State, the Oregon almost did not use poison chemicals. Although the Florida use the poison chemicals, they only use about 0.45%. From percent_posion_state table, over 30 percent chemicals using in CA is poison chemicals which is risky for human health. 

```{r}
Posion_state_per_years <- Posion_chem %>% group_by(State,Year) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
Posion_state_per_years$`State per Year` <- paste(Posion_state_per_years$State, Posion_state_per_years$Year, sep = " ")

ggplot(Posion_state_per_years, aes(x = `State per Year`, y = log(LB_sum)))+geom_bar(stat = "identity")+coord_flip()+ylab("log Pound of Each State Producation per year with Posion Chemicals ")
```
In this Plot, from 2016 to 2021, the poison chemicals application in California still maintain at very high levels. Compared to California, the poison chemicals application in Florida is much lower than California and in 2021 the Florida did not use posion chemicals at all. Meanwhile, I find the quantity of California strawberry is extremely higher than others States, based on two plots, so in next I would like find the proportion of strawberry quantity by State.
## Strawberry Proportion by State

```{r}
strawb5 <- strawb4 %>% pivot_wider(names_from = `units`, values_from = `Value`)
CWT <- ifelse(strawb5$` MEASURED IN CWT`=="(D)",0,strawb5$` MEASURED IN CWT`)
CWT_LB <- as.numeric(CWT)*100
strawb5$` MEASURED IN LB`[1:54]<- CWT_LB
LB_all <- ifelse(strawb5$` MEASURED IN LB`=="(D)"|strawb5$` MEASURED IN LB`=="(Z)"|
         strawb5$` MEASURED IN LB`=="(NA)",0,strawb5$` MEASURED IN LB`)
strawb5$` MEASURED IN LB` <- as.numeric(LB_all)
fresh_rows <-  grep("FRESH MARKET", strawb5$type2, ignore.case = T)
procss_rows <-  grep("PROCESSING", strawb5$type2, ignore.case = T)
strawb5 <- strawb5[-c(fresh_rows,procss_rows),]
total_rows1 <- grep("(TOTAL)", 
strawb5$`Domain Category`, ignore.case = T)
fertlizer_rows <- grep("FERTILIZER",strawb5$`Domain Category`, ignore.case = T)
organic_rows1 <- grep("ORGANIC",strawb5$type, ignore.case = T)
strawb5 <- strawb5[c(total_rows1,fertlizer_rows,organic_rows1),]
strawb5 %>% group_by(State) %>% summarise(LB = sum(` MEASURED IN LB`, na.rm = TRUE))

```

```{r}
total_state_LB <- strawb5 %>% group_by(State) %>% summarise(LB = sum(` MEASURED IN LB`, na.rm = TRUE))
ggplot(total_state_LB, aes(x="", y=LB, fill=State)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("Total Strawberries Production in Pound by State")
```
This Pi plot responds to my previous opinion, in this data sets, the California produce over 90% Strawberry. From my percentage poison chemicals by State, there are 
20192300 LB strawberry may harm human health. Therefore, there are at least 6% strawberry produced in California, which are harmful. 
```{r}
ggplot(total_state_LB, aes(x="", y=log(LB), fill=State)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("Total Strawberries Production in Pound by State")
```
This last figure, I log the value of production of strawberry in order to find the 
proportion of other State without California. This Pi chart show the Florida production is relatively higher than other states. Others production is closes with each others beside California. 
```{r}
ggplot(total_state_LB, aes(x=State, y=log(LB))) + 
  geom_bar(stat = "identity") + theme(legend.position="none")
```
