---
title: "strawberry"
author: "Tao Guo"
date: "2022-11-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(readxl)
library(ggplot2)
```

## Cleaning data

Separate the column of Data Item

```{r cars}
strawb <- read_xlsx("strawberries-2022oct30-a.xlsx",col_names = TRUE)
## separate the Data Item 
strawb2 <- strawb %>% separate(col=`Data Item`,
                               into = c("Strawberries", "items"),
                               sep = "-",
                               fill = "right")
strawb2 %<>% separate(col = `Strawberries`, into = c("Strawberries", "type", "type2"), 
                      sep = ",", fill = "right")
strawb3 <- strawb2 %>% separate(col = `items`, into = c("sale type", "units"), 
                                sep = ",", fill = "right")

strawb4 <- strawb3 %>% select(-c(4, 8:13, 15, 17))
```

1.  Build organic and non organic tibble

```{r}
Domain_organic1 <- grep("organic", 
                       strawb4$Domain, 
                       ignore.case = T)

org_rows1 <- Domain_organic1
strawb_organic <- strawb4 %>% slice(org_rows, preserve = FALSE)

strawb_non_organic <- strawb4 %>% filter(!row_number() %in% org_rows)
```

```{r}
strawb_non_organic %<>% pivot_wider(names_from = `units`, values_from = `Value`)
strawb_organic %<>% pivot_wider(names_from = `units`, values_from = `Value`)
```

2.  From non organic, separate the chemical tibble

```{r}
chem_rows <- grep("BEARING", 
                       strawb_non_organic$type, 
                       ignore.case = T)
chem_rows_1 <- grep("chemical", 
                  strawb_non_organic$Domain, 
                  ignore.case = T)
## chem_rows and chem_row_1 different rows
## firstly I guess the fertilizer in have BEARING is type column, but It is not in Domain 
chem_rows_f <- grep("FERTILIZER", strawb_non_organic$Domain)
intersect(chem_rows_f, chem_rows)
```

```{r}
strawb_chem <- strawb_non_organic %>% slice(chem_rows, preserve = FALSE)
strawb_chem
```

## Poison chemical Carbendazim, Bifenthrin, methyl bromide, 1,3-dichloropropene, chloropicrin, Telone

Searching the Poison chemical mentioned in reading

```{r}
#empty
df_carbendazim <- grep("carbendazim", 
                       strawb_chem$`Domain Category`, ignore.case = T)
df_Bifenthrin <- grep("Bifenthrin", 
                       strawb_chem$`Domain Category`, ignore.case = T)
df_methyl_bromide <- grep("methyl bromide", 
                      strawb_chem$`Domain Category`, ignore.case = T)
#empty
df_1_3_dichloropropene <- grep("1,3-dichloropropene", 
                          strawb_chem$`Domain Category`, 
                          ignore.case = T)
df_chloropicrin <- grep("chloropicrin", 
                               strawb_chem$`Domain Category`, ignore.case = T)
## empty
df_Telone <- grep("Telone", 
                        strawb_chem$`Domain Category`, 
                        ignore.case = T)
```

## Tibble for posion chemicals

The carbendazim, 1_3\_dichloropropene, and Telone did not find in table

```{r}
Bifenthrin <- strawb_chem[df_Bifenthrin,]
methyl_bromide <- strawb_chem[df_methyl_bromide,]
dichloropropene <- strawb_chem[df_chloropicrin,]

```

## Total Posion chemicals by State

```{r}
Posion_chem <- strawb_chem[c(df_Bifenthrin,df_methyl_bromide,df_chloropicrin ),]


```

I replace (D) to zero

```{r}
LB <- ifelse(Posion_chem$` MEASURED IN LB`[1:16]=="(D)",0, Posion_chem$` MEASURED IN LB`[1:16])
LB <- as.numeric(LB)
Posion_chem$` MEASURED IN LB` <- LB
Posion_chem %>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
```

### total chemical using by State

```{r}
LB_total <- ifelse(strawb_chem$` MEASURED IN LB`[1:728]=="(D)"|strawb_chem$` MEASURED IN LB`[1:728]=="(NA)"|strawb_chem$` MEASURED IN LB`[1:728]=="(Z)",0,strawb_chem$` MEASURED IN LB`[1:728])
strawb_chem$` MEASURED IN LB` <- as.numeric(LB_total)
strawb_chem%>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
```

## Percentage poison chemicals by State

```{r}
Posion_state <- Posion_chem %>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))
chem_state <- strawb_chem%>% group_by(State) %>% summarise(LB_sum = sum(` MEASURED IN LB`))

Posion_state$Total_LB <- chem_state$LB_sum
Posion_state %>% mutate(Percent_posion = LB_sum/Total_LB)
percent_posion_state <- Posion_state %>% mutate(Percent_posion = LB_sum/Total_LB)
```

```{r}
percent_posion_state1 <- percent_posion_state[-4] %>% pivot_longer(c(LB_sum,Total_LB), names_to = "type",values_to = "value")
```

```{r}
ggplot(percent_posion_state1, aes(fill=type, y=log(value+1), x=State)) + 
    geom_bar(position="dodge", stat="identity")+ylab("log scale of Measure in LB")+
  ggtitle("Poison Chemicals and Total Chemicals by State")+
  scale_fill_discrete(labels = c("Poison Chemicals","Total Chemicals"))
```

From this plot, The California high weight of poison chemicals than other State, the Oregon almost did not use poison chemicals From percent_posion_state table, over 20 percent chemicals using in CA is poison chemicals which is risky for human health. Meanwhile, I find the quantity of California strawberry is extremely higher than others States, so in next I would like find the proportion of strawberry quantity by State. \## Strawberry Proportion by State

```{r}
strawb5 <- strawb4 %>% pivot_wider(names_from = `units`, values_from = `Value`)
CWT <- ifelse(strawb5$` MEASURED IN CWT`=="(D)",0,strawb5$` MEASURED IN CWT`)
CWT_LB <- as.numeric(CWT)*100
strawb5$` MEASURED IN LB`[1:54]<- CWT_LB
LB_all <- ifelse(strawb5$` MEASURED IN LB`=="(D)"|strawb5$` MEASURED IN LB`=="(Z)"|
         strawb5$` MEASURED IN LB`=="(NA)",0,strawb5$` MEASURED IN LB`)
strawb5$` MEASURED IN LB` <- as.numeric(LB_all)
strawb5 %>% group_by(State) %>% summarise(LB = sum(` MEASURED IN LB`, na.rm = TRUE))

```

```{r}
total_state_LB <- strawb5 %>% group_by(State) %>% summarise(LB = sum(` MEASURED IN LB`, na.rm = TRUE))
ggplot(total_state_LB, aes(x="", y=LB, fill=State)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("Total Strawberries Production in Pound by State")
```

This figure show the California produced a extraordinary quantity of strawberries compare to other states.

```{r}
ggplot(total_state_LB, aes(x="", y=log(LB), fill=State)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0)+theme_void()+ggtitle("Total Strawberries Production in Pound by State")
```

```{r}
ggplot(total_state_LB, aes(x=State, y=log(LB))) + 
  geom_bar(stat = "identity") + theme(legend.position="none")
```
